\chapter{Project Rules}
This chapters details the internal rules the group follows. This includes types of the meetings that will be conducted (\autoref{sec:meetings}), as well as a schedule of a typical workday in the project (\autoref{sec:day-to-day-structure}).

\section{Internal/External Meetings}
\label{sec:meetings}
Internal meetings constitute debriefs at the beginning and end of each workday. A daily debrief work as follows: in the morning, each member shall discuss what they are going to work on; in the evening, everyone shall reflect on the extend to which those tasks have been accomplished. The allocated debrief time of fifteen minutes is a maximum, depending on the stage of the project, the debriefs may take less time.

The external meetings consist in the largest part of weekly status meetings with the group tutor and coaches, during which updates on the group progress are given to the tutor and questions the group has encountered are addressed. There are also formal meetings for the baseline, midterm and final review, which require significant beforehand preparation and as such have been included in the Gantt Chart(\autoref{fig:gantt_chart}). As of now, in-person meetings with the external stakeholders are not planned and the communication will proceed via email.

\section{Day-to-day structure}
\label{sec:day-to-day-structure}
The working hours for the project are 8.30 a.m. to 5.30 p.m. every business day in the Netherlands during the project duration. This time interval includes breaks, as well as debrief time at the beginning and end of the work day. The schedule of those is defined in \autoref{tab:break-debrief-times}. The total work time per day (excluding the 1 hour in total of breaks) is 8 hours.




\begin{table}[h]
    \centering
        \caption{Break and debrief time during the day}
    \begin{tabular}{|c|c|c|}
        \hline
         \textbf{Event}& \textbf{Start} & \textbf{End}\\ \hline
         \hline
         Morning Debrief& 8:30 a.m.  & 8:45 a.m. \\ \hline
         Morning Break& 10:30 a.m.  & 10:40 a.m. \\ \hline
         Lunch Break& 12:00 p.m. & 12:40 p.m.\\ \hline
         Afternoon Break& 3:30 p.m. & 3:40 p.m. \\ \hline
         Evening Debrief& 5:15 p.m. & 5:30 p.m.\\ \hline
    \end{tabular}
    \label{tab:break-debrief-times}
\end{table}

