\chapter{Profitability and return analysis}
To estimate the profitability and return of the HUGO, it is necessary to determine how often is the aircraft going to be utilized. The duration of one flight test is expected to be 30 minutes and multiple flight tests can be conducted during a test day. A reference test day was determined to include four test flights. It is assumed that the UAV will be utilized and actively operational 100 days a year. This is determined from all working days in a year with a 20\% downtime due to maintenance, 60\% of days available with favourable weather conditions, and 80\% usage of remaining days.
\section{Market price}
It has been decided that the UAV will be made available to customers by leasing. A customer will pay a fee determined by the number of flight days, analogous to a typical wind tunnel financial model. In the price of a typical flight day, all consumables and operations costs are included. These costs are estimated at \texteuro{450} per typical flight day. Additionally, a fraction of the UAV production, insurance, certification and total 15-year maintenance price is included to return the one-time and per aircraft expenses in the period of 3 years, i.e. 300 flight days. Maintenance cost fractions are based on the expected usage over 15 years, i.e. 1500 flight days with 2 flight hours each. Based on the derived costs, 292 € of profit is needed to break even in 3 years. Overview of the costs considered can be seen in \autoref{tab:costs}. Detailed description of the costs is present in the subsequent sections.

\section{Market share and volume} 
To calculate the market share and volume, three main markets were considered; Total Addressable Marker (TAM), Serviceable Addressable Market (SAM), Serviceable Obtainable Market (SOM). The total global market for aeronautical testing is reported at \$6.94B in 2026, with a compounded annual growth rate of 7.28\% until 2035, representing the TAM \footnote{\href{https://www.businessresearchinsights.com/market-reports/aeronautical-tester-market-105709}{Aeronautical testing market}(accessed on 24.04.2026)}. A more accessible early market is the European aerospace wind tunnel testing market, reported at \$ 1B \footnote{\href{https://www.prophecymarketinsights.com/market_insight/europe-wind-tunnel-market-5840}{European Aerospace wind tunnel testing market}(accessed on 24.04.2026)}. 

The Netherlands was chosen as the beachhead market, representing the SAM. Public data for the aerospace component testing market was not available. Consequently, two approaches were used to estimate the total relevant Dutch market size. First, a top-down approach starting with the entire Dutch economy, and narrowing to aviation, and aerospace engineering R\&D, and finally wind tunnel testing \footnote{\href{https://www.iata.org/en/iata-repository/publications/economic-reports/the-value-of-air-transport-to-the-netherlands/}{Top-Down}(accessed on 24.04.2026)}. However, this methodology could not provide reasonable estimates relative to the TAM. The bottom-up approach proved much more successful. First, by finding the largest players in the Aerospace component testing industry in the Netherlands, and approximating their total budget for testing on wind tunnels and aircraft like the PH-LAB. The NLR, TU Delft, and NDW were identified as the major players. The TU Delft's total yearly operating costs of the nine wind tunnel facilities were approximated using publicly available data from NASA's wind tunnels in 2012, and adjusting for inflation, as the TU Delft does not report its own operating costs \footnote{\href{https://www.tudelft.nl/lr/organisatie/afdelingen/flow-physics-and-technology/facilities}{TU Delft wind tunnel facilities}(accessed on 24.04.2026)}\footnote{\href{https://www.nasa.gov/wp-content/uploads/2023/06/nasa-wind-tunnels-final-report-20150813-tagged.pdf}{NASA Wind Tunnels}(accessed on 24.04.2026)}\footnote{\href{https://www.in2013dollars.com/us/inflation/2012?amount=1}{Inflation Calculator}(accessed on 24.04.2026)}. Then, the total operating cost of the PH-LAB was calculated by extrapolating the total flight time of the last three months from publicly available flight logs, and comparing with standard operating costs of the Cessna Citation 550 \footnote{\href{https://www.flightaware.com/live/flight/PHLAB/history}{PH-LAB flight history}(accessed on 24.04.2026)}\footnote{\href{https://www.libertyjet.com/jet-ownership-costs.aspx?jetType=CE-550}{Cessna Citation 550 Operational costs}(accessed on 24.04.2026)}. The NLR also does not make operational costs freely available. Thus, the operational cost breakdown of the DLR was used, and applied to the NLR \footnote{\href{https://www.government.nl/topics/taxation-and-businesses/corporation-tax}{DLR Budget}(accessed on 24.04.2026)}\footnote{\href{https://craft.co/nlr}{NLR Budget}(accessed on 24.04.2026)}. DNW's funding and operating costs are also not available, so an estimate for their budget was found, and the share of wind tunnels in the Netherlands was used to proportionally divide the testing budget \footnote{\href{https://www.lusha.com/business/2bd3ebff838fff84/}{DNW Budget}(accessed on 24.04.2026)}\footnote{\href{https://www.dnw.aero/wind-tunnels/}{DNW Wind Tunnels}(accessed on 24.04.2026)}. These were then summed resulting in a SAM of approximately \texteuro{71M} \autoref{APPENDIX TBD}. 

Realistically, not all experiments can be performed on the HUGO platform. Estimating 20\% of the SAM can be replaced by HUGO, the SOM is thus \texteuro{14.2M} in 2026.

As explained in \autoref{APPENDIX TBD}, several assumptions were made regarding the operational costs and total aerospace testing budgets used in the SAM. However, estimates such as using the operational costs instead of client test costs, the final SAM and SOM represent a conservative estimate, and are likely to be larger than reported.

\section{Development costs}
All development costs used for the profit and market price calculations are shown in \autoref{tab:costs}
\subsection{Labour costs}
This aircraft is actively developed by TU Delft students. Therefore, the human labour costs associated with the project development, such as tasks associated with design, testing and manufacturing, are not included.

\subsection{Certification costs}
The UAV will be subject to several airworthiness certification procedures. First, the operator of the aircraft has to be registered in The Netherlands under the RDW authority to get authorized for operating UAVs. The cost of this administrative action is approximately \texteuro{50} \footnote{\href{https://www.portofrotterdam.com/sites/default/files/2025-07/regulation-and-permit-application-drones.pdf}{Port Rotterdam Regulations}(accessed on 24.04.2026)}. Flying a UAV in the specific category under EASA regulation requires permit from the ILT. The fee for this procedure usually lies below \texteuro{10,000} \footnote{\href{https://www.rdw.nl/en/drone/applying-for-a-pilot-licence-or-operator-number-for-a-drone}{Applying for a pilot licence or operator number for a drone | RDW}(accessed on 24.04.2026)}. A cost of \texteuro{5,000} is estimated here. 

\section{Production costs}
The total production cost of the aircraft is heavily dependent on the materials and resources used. The maxium cost per unit is capped at \texteuro{45,000}. Among the direct costs of the materials used, production expenses should also include costs of facility use and direct labour costs. An initial estimate of 300 man-hours at a wage of \texteuro{50} per hour is used. The UAV production process is estimated to last two working weeks (e.g. 10 working days) with a total facility use expense of \texteuro{2,000} (i.e. \texteuro{200} per day).

\section{Direct operational costs}
Operations of the UAV include several categories of expenses, including fuel and energy costs, transport costs, insurance costs and labour costs.
\subsection{Fuel and energy costs}
In order to perform a 30-minute test flight, around 11.5 litres of SAF needs to be used. This is based on the average consumption of one VULCAN engine. Considering a SAF price of \texteuro{}{2768} per ton \footnote{\href{https://www.easa.europa.eu/en/domains/environment/eaer/sustainable-aviation-fuels/saf-market#saf-price}{EASA}(accessed on 24.04.2026)}, at a density of 800 $kg \cdot m^{-3}$, the price per liter of SAF lies at \texteuro{2.2} per liter. Therefore, the fuel cost per one test flight can be estimated at \texteuro{30}. Other energy involved in the process includes electricity used for charging the UAV batteries and powering computers and hardware needed to conduct the test. In general, these costs will be low. An extra margin of \texteuro{20} per test flight is added to the total energy cost which accounts for a sufficient margin.
\subsection{Transport costs}
Transport costs represent expenses associated with transporting the aircraft to the test site. This includes fuel or energy used by the transport vehicle and potential cost of leasing a vehicle or hiring an external driver. Assuming that the aircraft is mostly going to be used for testing within The Netherlands, these costs can be estimated at \texteuro{250} per test.
\subsection{Insurance costs}
Since the aircraft will have a maximum take-off mass larger than 20 kg, legislation requires arranging a third-party insurance. The annual price of insurance for a similar-sized UAV usually ranges from lower to higher hundreds of Euros \footnote{\href{https://droneland.nl/insurance?___store=en}{DroneLand}(accessed on 24.04.2026)}. Therefore, an estimate of an annual price of 500 € has been used.
\subsection{Maintenance costs}
During its operational life, the UAV will need regular maintenance to remain operational. First, the VULCAN engine should be regularly maintained. For turbines of similar size, such as the Hybl H20PRO, the maintenance interval is around 50 hours \footnote{\href{https://www.hyblturbines.cz/h16bl/}{H20PRO}(accessed on 24.04.2026)}. This includes inspection and occasional part replacement (e.g. bearings or spark plugs). Therefore, \texteuro{250} for every 50 operational hours of the VULCAN engine are included for maintenance costs. The maintenance of the airframe is heavily dependent on the use case. It is assumed that the airframe will not require serious maintenance over its whole operational lifetime. A fixed expense of \texteuro{500} for every 100 flight hours is accounted for to allow for inspection, battery replacement and minor repairs.

\begin{table}[H]
    \centering
    \caption{Overview of UAV costs and their contribution to flight day pricing}
    \begin{tabular}{|l|l|l|c|r|}
        \hline
        \textbf{Type} & \textbf{Subcategory} & \textbf{Description} & \textbf{Pricing Role} & \textbf{Cost (€)} \\ \hline
        
        \multicolumn{5}{|c|}{\textbf{Direct costs, reference flight day}} \\ \hline
        Operations & Turbine fuel & 11.5 L of SAF, 4 test flights & Direct & 120 \\ \hline
        Operations & Electricity & Batteries, computers, systems & Direct & 80 \\ \hline
        Operations & Transport & Vehicle + logistics & Direct & 250 \\ \hline
        Operations & Mission & UAV pilot/operator & Direct & 400 \\ \hline
        
        \multicolumn{5}{|c|}{\textbf{Fractional costs, full return in 300 flight days}} \\ \hline
        Certification & RDW + ILT & Registration and flight permits & Fraction & 5\,000 \\ \hline
        
        Production & Materials & UAV structural and system components & Fraction & 28\,000 \\ \hline
        Production & Labour & 300 h at 50 €/h & Fraction & 15\,000 \\ \hline
        Production & Facility & 10 days at 200 €/day & Fraction & 2\,000 \\ \hline
        
        Operations & Insurance & 500 € annually, 15 years total & Fraction & 7500 \\ \hline
        
        Maintenance & Engine & 250 € per 50 h, 3000 h total & Fraction & 15000 \\ \hline
        Maintenance & Airframe & 500 € per 100 h, 3000 h total & Fraction & 15000 \\ \hline
        
    \end{tabular}
      \label{tab:costs}
\end{table}

