\chapter{Project Objectives}

Project objectives are specific, measurable, actionable, relevant, and time-bound (SMART) outcomes a project intends to deliver. 

\section{Financial}
The financial objectives focus on the budget management and profitability of the project. 

\begin{enumerate}
    \item The total manufacturing cost per aircraft configuration shall not exceed 45k€, including development, materials, propulsion system, avionics, and assembly, as verified at the end of the prototype build phase.

    \item The aircraft shall have an operational cost of no more than TBD€ per flight hour, including fuel, maintenance, and consumables, measured during flight testing.
    \todo{research typical wind tunnel running costs}

    \item The aircraft shall be capable of at least TBD flight hours before requiring a major overhaul, ensuring lifecycle cost efficiency (maybe that is more of a performance objective?).

    \item Critical components shall be replaceable at a cost not exceeding TBD\% of total system cost, enabling economically viable maintenance (can we estimate this?).
\end{enumerate}

\section{Quality}
The quality objectives are used to define standards for the deliverables.

\begin{enumerate}
    %\item All sensors shall achieve an accuracy within $\pm$ TBD\% across the operational flight envelope, as validated during flight testing.

    %\item All sensors shall maintain a data availability of at least TBD\% during the duration of a test flight.

    %\item All sensors shall provide measurements at a minimum update rate of TBD Hz during operation.

    \item Repeated measurements under identical atmospheric conditions shall not deviate by more than $\pm$ TBD\%.

    \item The aircraft shall achieve a minimum of TBD flight hours between critical failures (MTBF).

    \item Data shall be stored in a standardized format compatible with analysis tools.

    \item The aircraft shall ensure lossless acquisition and storage of all payload sensor data during flight operations, with data loss not exceeding TBD\%.

    \item The aircraft shall provide mounting integration of external sensors without requiring modification of core flight control systems.
    
\end{enumerate}

\section{Performance}
The performance objectives focus on the results and effectiveness of the project.

\begin{enumerate}

    \item The aircraft shall enable the collection of valid flight test data at 0.75 Mach for at least TBD minutes at an altitude of TBD m per mission.

    \item The aircraft shall enable the collection of valid flight tests at an airspeed $\ge$ 0.4 Mach for at least TBD minutes at an altitude of TBD m per mission.

    \item The aircraft shall enable the integration and operation of payloads of at least 5 kg and 5 L to support its intended flight test and data acquisition missions.

    \item The aircraft configuration shall allow execution of at least TBD repeatable flight test conditions per mission.

    \item The UAV shall demonstrate a minimum operational range of TBD km using a constrained flight test profile (out-and-back) within regulated airspace.

\end{enumerate}

\section{Business}
The business objectives align with strategic goals like increased revenue or market share.

\begin{enumerate}
    \item The project shall achieve a positive cumulative net financial result within TBD months after initial operational deployment, based on total development and operational costs relative to generated revenue, as verified through financial reporting (or alternatively specify the revenue value to be generated).

    \item The project shall achieve a market share of TBD\% within the defined target market of universities, research centers, and aircraft companies within TBD months after initial operational deployment, measured based on the number of systems deployed or contracted.

    \item The UAV system shall be ready for initial operational deployment within TBD months from project start.

    \item The project shall achieve adoption by at least TBD external research groups, institutions, or industry partners within TBD months after initial operational deployment (ig important for adoption, but sounds kinda over the top).
    
\end{enumerate}

\section{Compliance}
The compliance objectives ensure adherence to regulations and standards.

\begin{enumerate}
    \item The UAV system shall demonstrate compliance with applicable airworthiness and safety requirements for unmanned aircraft, including fail-safe and emergency procedures, prior to deployment.
    %\todo{look up specific requirements that apply for us and include them}

    \item All communication systems shall comply with applicable radio frequency regulations and spectrum usage requirements within the region of operation.

    \item The UAV system shall comply with applicable environmental regulations, including noise and emissions limits, within the intended operational environment.
    %\todo{again, check these}

\end{enumerate}


