\chapter{Requirements}

\begin{longtable}{|p{3cm}|p{11cm}|}
\caption{Top-level aircraft requirements}
\label{tab:system_requirements} \\
\hline
\textbf{Requirement ID} & \textbf{Requirement} \\
\hline
\endfirsthead

\hline
\textbf{Requirement ID} & \textbf{Requirement} \\
\hline
\endhead

GEN-001 & The total mass shall not be larger than 50 kg. \\ \hline
GEN-002 & The total cost of a single configuration shall not exceed 45k€. \\ \hline
GEN-003 & The available payload mass shall be larger than 5 kg. \\ \hline
GEN-004 & The VULCAN engine shall be used by all aircraft configurations. \\ \hline

PER-001 & The range at maximum payload shall be longer than TBD. \\ \hline
PER-002 & The endurance at maximum payload shall be longer than 30 minutes. \\ \hline
PER-003 & The aircraft shall be able to reach Mach 0.75. \\ \hline
PER-004 & The shall be able to sustain the speed faster than Mach 0.4 during the main flight stage. \\ \hline

AER-001 & The critical Mach number shall be higher than 0.75. \\ \hline

OPS-001 & The lifetime of a single configuration shall be longer than 15 years. \\ \hline
OPS-002 & All regular service, required parts, and tools shall fit within a van-sized vehicle. \\ \hline
OPS-003 & It shall be possible to maintain the aircraft on a regular basis. \\ \hline

CER-001 & The aircraft shall not exceed an altitude of TBD. \\ \hline
CER-002 & It shall be possible to safely recover the aircraft in all flight scenarios. \\ \hline

SUS-001 & The aircraft shall use sustainable aviation fuel (SAF). \\ \hline
SUS-002 & The aircraft shall be recyclable. \\ \hline

CON-001 & The aircraft shall be capable of autonomous flight. \\ \hline
CON-002 & The aircraft shall be fully controllable remotely. \\ \hline

STA-001 & The aircraft shall be capable of stable, neutral, and unstable flight conditions. \\ \hline

STR-001 & The structure shall withstand transonic loads. \\ \hline
STR-002 & The structure shall allow integration of the VULCAN engine. \\ \hline
STR-003 & The structure shall accommodate a payload bay of at least 5 litres. \\ \hline
STR-004 & The structure shall accommodate space for a secondary flight computer. \\ \hline
STR-005 & The wing, tail, and payload bay shall be modular. \\ \hline
STR-006 & The aircraft shall provide interfaces for mounting sensors and actuators. \\ \hline

\end{longtable}