\chapter{Certification}
This chapter focuses on the process and the steps required to obtain the certification of HUGO to be used for the research purpose of testing the aeroelastic effects of high aspect ratio wings. In the first section (cite) the classification process is described that places HUGO into a type class category. Following the assessment of flight class, the certification for a Design Organisational Approval (DOA) is covered, where the different wings' and tail designs are considered.

\section{Type Certificate}

\section{Design Organisational Approval (DOA)}
For the certification procedure of an aircraft, the competent authority in Europe, EASA, requires extensive documentation and validation procedures of the design. This is a stage in the design of the UAV, where certain restrictions have to be taken into account for its operation, such as airworthiness class and operational enviromets.

Certification of an aircraft, or of modifications brought to it, involves contacting EASA si they can take the following steps\footnote{\href{https://www.easa.europa.eu/en/domains/aircraft-products/aircraft-certification?}{EASA Aircraft Certification}}

\begin{itemize}
    \item Technical familiarisation and certification basis
    \item Establishment of the certification programme
    \item Compliance demonstration
    \item Technical closure and issue of approval
\end{itemize}

Costs involved in this process and the time required for analysis of the design are not well defined, but can range from months to years, depending on the complexity of the idea. This conflicts with HUGOs' mission, whitch requires it to be able to fly with new modifications to its structure each time. Since the recertification process is applied for any modifications, this would result in an excess of downtime of the UAV, loss in revenue and \textcolor{red}{A VERY SAD SULTAN}, loss of purpose of such a platform.

EASA classifies that a new recertification for the aircraft is required each time a change is implemented, such changes further falling into 2 types: \textbf{Minor changes} and  \textbf{Major Changes}. A \textbf{Minor change} is classified as any type of modiffication that does not show any appreciable effect on weighrt, structura strengh, reliability and other specifications as found in  

To avoid having to recertify the aircraft for each design mo

The process is applied each time a "major" modification (a defined by EASA in \todo{cite EASA major and minor modifications}) is applied to the aircraft. This condition directly conflicts with the modularity requirement of HUGO. By having a modular configuration, HUGO will be susceptible to regular structural changes of the wings, which are considered major modifications by EASA and are subject to recertification. 

DOA is a certification that allows the organisation a certain degree of freedom when it comes to certifications and decisions of some aspects of design and operations. 
%\subsection{DOA Implications}


%\subsection{Application Procedure and Documentation}

\section{V-n diagram}
Based on \cite{EASA_CSVLA_Amend1}.